Transfer Learning in Visual and Relational Reasoning

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/transfer_learning.tex
work on experiments, up to reasoning transfer
Signed-off-by: ibm <tkornuta.ibm@gmail.com>
minor change to TL

\section{Transfer Learning}
\label{sec:transfer_learning}
\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{../img/architecture/transfer_taxo}
	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
\end{figure*}
Due to the complex nature of visual reasoning, it appears that
transfer learning from a source domain to a target domain can be investigated in
multiple ways, depending on how the two domains are related. This includes visual attributes such as size, color and shape, temporal characteristics reflected in the number of frames and scene complexity, and finally the reasoning difficulty. 
To establish a formal framework for these various aspects, we first recall the basic definition of transfer learning~\cite{pan2009survey}.

@@

We now formally define 3 kinds of transfer learning problems, namely,
\emph{feature transfer}, \emph{temporal transfer},
and \emph{reasoning transfer}.
These are illustrated in~\cref{fig:taskonomy} using representative examples from CLEVR-CoGenT and COG datasets that are particularly suited for experimental
investigations of transfer learning.
In \cref{sec:experiments}, we detail the performance of
SAMNet for each of these 3 kinds, using the CLEVR-CoGenT dataset
for feature transfer, the COG dataset for temporal transfer, and finally
both datasets for reasoning transfer, with appropriate baseline comparisons.

Let $\cQ$ and $\cV$ denote the set of questions and visual inputs, respectively.
\begin{description}
	%\compresslist % used to reduce spacing
	\item[Feature Transfer:] In this setting of domain adaptation, $\cX_S = \cX_T \subseteq \cQ \times \cV$
	and the task $f(q,v)$ is just the answer to the question $q$ on visual input $v$. The output set $\cY$ is the union of legitimate answers
	over all questions in $\cQ$.
	The marginal distributions $P_S$ and $P_T$ differ in the feature attributes such as shape, color, and size, or their combinations
	thereof.

>>>>

\section{Transfer Learning}
\label{sec:transfer_learning}
\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{../img/architecture/transfer_taxo}
	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
\end{figure*}
Due to the complex nature of visual reasoning, it appears that
transfer learning from a source domain to a target domain can be investigated in
multiple ways, depending on how the two domains are related. This includes visual attributes such as size, color and shape, temporal characteristics reflected in the number of frames and scene complexity, and finally the reasoning difficulty. 
To establish a formal framework for these various aspects, we first recall the formal notions in the framework of transfer learning~\cite{pan2009survey}.

@@

We now formally define 3 kinds of transfer learning problems, namely,
\emph{feature transfer}, \emph{temporal transfer},
and \emph{reasoning transfer}.
These are illustrated in~\cref{fig:taskonomy} using representative examples from CLEVR-CoGenT and COG datasets that are particularly suited for experimental
investigations of transfer learning.
%In \cref{sec:experiments}, we detail the performance of SAMNet for each of these 3 kinds, using the CLEVR-CoGenT dataset for feature transfer, the COG dataset for temporal transfer, and finally both datasets for reasoning transfer, with appropriate baseline comparisons.
Let $\cQ$ and $\cV$ denote the set of questions and visual inputs, respectively.
\begin{description}
	%\compresslist % used to reduce spacing
	\item[Feature Transfer:] In this setting of domain adaptation, $\cX_S = \cX_T \subseteq \cQ \times \cV$
	and the task $f(q,v)$ is just the answer to the question $q$ on visual input $v$. The output set $\cY$ is the union of legitimate answers
	over all questions in $\cQ$.
	The marginal distributions $P_S$ and $P_T$ differ in the feature attributes such as shape, color, and size, or their combinations
	thereof.
